---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

![theme_park_banner](https://github.com/MatthewBJane/theme_park/assets/52077481/4c2e2885-d879-46e6-b61d-b253d8382597)

# ThemePark

<!-- badges: start -->
<!-- badges: end -->

# Welcome to the Theme Park
Theme Park is a package for fun ggplot themes related to popular culture (movies, TV shows, video-games, etc.). I don't have much time to expand this further so please consider submitting a theme!

## Submit a Theme
Please help grow this package by submitting your own custom ggplot theme for a movie, show, or videogame. To submit, edit the [`R/theme_template.R`](R/theme_template.R) script file and send the edited script to matthew.jane@uconn.edu or submit a pull request. I will review it and add it or respond with suggested edits. Have fun with it!

## Themes contributed

Name | Theme | Creator(s) |
---- | ----- | ---------- |
**Barbie** | `theme_barbie` | Matthew B. Jané |
**Oppenheimer** | `theme_oppenheimer` | Matthew B. Jané & Toki Liam |
**Star Wars** | `theme_starwars` | Matthew B. Jané |
**Zelda** | `theme_zelda` | Alex Slavenko |
**Terminator** | `theme_terminator` | Alex Slavenko |
**Spiderman** | `theme_spiderman` | Velu P.K. Immonen |
**Avatar** | `theme_avatar` | Velu P.K. Immonen |
**Gryffindor** | `theme_gryffindor` | Begum Ozemek |
**Hufflepuff** | `theme_hufflepuff` | Begum Ozemek |
**Ravenclaw** | `theme_ravenclaw` | Begum Ozemek |
**Slytherin** | `theme_slytherin` | Begum Ozemek |
**Futurama** | `theme_futurama` | Tylor J. Harlow |
**Simpsons** | `theme_simpsons` | Tylor J. Harlow |
**Lord of the Rings** | `theme_lordoftherings` | Ethan Milne |
**Game of Thrones** | `theme_gameofthrones` | Brennan Antone |
**Godfather** | `theme_godfather` | Francisco Garre-Frutos |
**Finding Nemo** | `theme_nemo` | Christopher T. Kenny |
**Friends** | `theme_friends` | Alexis van STRAATEN |


## Installation

You can install the development version of `ThemePark` from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("MatthewBJane/theme_park")
```

## Example

There are many theme options, listed above. 

Below is an example of using the Game of Thrones theme.

```{r example}
library(ThemePark)
library(ggplot2)

`X variable` <- rnorm(50, 0, 1)
`Y variable` <- rnorm(50, 0, 1)

ggplot(data = NULL, aes(x = `X variable`, y = `Y variable`)) +
  theme_gameofthrones(gameofthrones_font = TRUE) +
  geom_smooth(method = "lm", color = "#8C4522", fill = "#DFCB69") +
  geom_point(color = "#BD6D33") +
  ggtitle("Game of Thrones Scatter Plot")
```

We can mix this with colors from the Barbie theme.

```{r cars}
g <- ggplot(mpg, aes(cty))
g + geom_density(aes(fill = factor(cyl)), alpha = 0.8) +
  labs(
    title = "Density plot",
    subtitle = "City Mileage Grouped by Number of cylinders",
    caption = "Source: mpg",
    x = "City Mileage",
    fill = "# Cylinders"
  ) +
  theme_gameofthrones() +
  scale_color_barbie()
```

```{r}
ggplot(data = NULL, aes(x = `X variable`, y = `Y variable`)) +
  theme_avatar(avatar_font = TRUE) +
  geom_smooth(method = "lm", color = "#1C3F6E", fill = "#5AACCF") +
  geom_point(color = "#2E67A0") +
  ggtitle("Avatar Scatter Plot")
```


```{r}
ggplot(data.frame(x = rnorm(100), y = rnorm(100)), aes(x, y)) +
  geom_smooth(method = "lm", color = "#912411", fill = "#912411") +
  geom_point(color = "#d3cfc3") +
  labs(title = "The Godfather theme", x = "Variable x", y = "Variable y") +
  theme_godfather(godfather_font = T)
```


## Citation

### BibTeX:
```
@software{JaneBarbie2023,
  author = {Jané, Matthew B},
  month = {6},
  title = {theme_park: popular culture ggplot themes},
  url = {https://github.com/MatthewBJane/theme_park},
  version = {1.0.0},
  year = {2023}
}
```
### APA:
Jané, M.B. (2023). theme_park: popular culture ggplot themes (Version 0.0.1) [Source Code]. https://github.com/MatthewBJane/theme_park
