---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.width = 6, height = 4, dpi = 150
)
set.seed(1234)
```

![theme_park_banner](https://github.com/MatthewBJane/ThemePark/assets/52077481/91916a23-e466-4dcb-b5c2-cb2c4fe55f04)

# ThemePark

<!-- badges: start -->
[![R-CMD-check](https://github.com/MatthewBJane/theme_park/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/MatthewBJane/ThemePark/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

# Welcome to the Theme Park
Theme Park is a package for fun ggplot themes related to popular culture (movies, TV shows, video-games, etc.). I don't have much time to expand this further so please consider submitting a theme!

## Submit a Theme
Please help grow this package by submitting your own custom ggplot theme for a movie, show, or videogame. To submit, edit the [`theme_template.R`](inst/theme_template.R) script file or run `ThemePark:::new_theme_park_theme()` and send the edited script to matthew.jane@uconn.edu or submit a pull request. I will review it and add it or respond with suggested edits. Have fun with it!

## Themes contributed

Name | Theme | Creator(s) |
---- | ----- | ---------- |
**Barbie** | `theme_barbie()` | Matthew B. Jané |
**Oppenheimer** | `theme_oppenheimer()` | Matthew B. Jané & Toki Liam |
**Star Wars** | `theme_starwars()` | Matthew B. Jané |
**Zelda** | `theme_zelda()` | Alex Slavenko |
**Terminator** | `theme_terminator()` | Alex Slavenko |
**Spiderman** | `theme_spiderman()` | Velu P.K. Immonen |
**Avatar** | `theme_avatar()` | Velu P.K. Immonen |
**Gryffindor** | `theme_gryffindor()` | Begum Ozemek |
**Hufflepuff** | `theme_hufflepuff()` | Begum Ozemek |
**Ravenclaw** | `theme_ravenclaw()` | Begum Ozemek |
**Slytherin** | `theme_slytherin()` | Begum Ozemek |
**Futurama** | `theme_futurama()` | Tylor J. Harlow |
**Simpsons** | `theme_simpsons()` | Tylor J. Harlow |
**Lord of the Rings** | `theme_lordoftherings()` | Ethan Milne |
**Game of Thrones** | `theme_gameofthrones()` | Brennan Antone |
**Godfather** | `theme_godfather()` | Francisco Garre-Frutos |
**Finding Nemo** | `theme_nemo()` | Christopher T. Kenny |
**Friends** | `theme_friends()` | Alexis van STRAATEN |
**Alien** | `theme_alien()` | Luke Pilling |
**Grand Budapest Hotel**| `theme_grand_budapest()` | Katya Kustova |
**Asteroid City** | `theme_asteroid_city()` | Katya Kustova |
**French Dispatch** | `theme_french_dispatch()`  | Katya Kustova |
**Moonrise Kingdom** | `theme_moonrise_kingdom()` | Katya Kustova |


## Installation

You can install the development version of `ThemePark` from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("MatthewBJane/ThemePark")
```

## Example

There are many theme options, listed above. You can see the list within your R session using:
``` {r}
library(ThemePark)
head(themepark_themes)
```

The Barbie theme (`theme_barbie()`) has been one of the most popular themes from `ThemePark`. Use it with the included dataset `barbie_box_office` like below:

```{r}
library(ggplot2)

# see suggested colours in the palette
barbie_theme_colors

# plot Box Office Takings (in million USD) over Days Since Release
ggplot(barbie_box_office |> dplyr::mutate(daily=daily/1000000), 
       aes(x = day, y = daily)) +
	geom_smooth(method = 'loess', 
	            color  = barbie_theme_colors["dark"],
	            fill   = barbie_theme_colors["light"]) +
	geom_point(color = barbie_theme_colors["medium"]) +
	labs(title = "Barbie Scatter Plot",
	     subtitle = "Daily box office takings",
	     caption  = "Source: www.boxofficemojo.com",
	     x = "Days since release",
	     y = "Box office takings (million USD)") +
	theme_barbie()
```


Below is an example of using the Game of Thrones theme.

```{r example}
# see suggested colours in the palette
gameofthrones_theme_colors

`X variable` <- rnorm(50, 0, 1)
`Y variable` <- rnorm(50, 0, 1)

ggplot(data = NULL, aes(x = `X variable`, y = `Y variable`)) +
  theme_gameofthrones(gameofthrones_font = TRUE) +
  geom_smooth(method = "lm",
              color = gameofthrones_theme_colors["dark"],
              fill = gameofthrones_theme_colors["light"]) +
  geom_point(color = gameofthrones_theme_colors["medium"]) +
  ggtitle("Game of Thrones Scatter Plot")
```

We can mix this with colors from the Barbie theme.

```{r cars}
g <- ggplot(mpg, aes(cty))
g + geom_density(fill = barbie_theme_colors["medium"]) +
    labs(
        title = "Density plot",
        subtitle = "City Mileage",
        caption = "Source: mpg",
        x = "City Mileage"
    ) +
    theme_gameofthrones()
```

```{r}
ggplot(data = NULL, aes(x = `X variable`, y = `Y variable`)) +
  theme_avatar(avatar_font = TRUE) +
  geom_smooth(method = "lm", color = avatar_theme_colors["dark"], fill = avatar_theme_colors["light"]) +
  geom_point(color = avatar_theme_colors["medium"]) +
  ggtitle("Avatar Scatter Plot")
```


```{r}
ggplot(data.frame(x = rnorm(100), y = rnorm(100)), aes(x, y)) +
  geom_smooth(method = "lm", color = godfather_theme_colors["dark"], fill = godfather_theme_colors["light"]) +
  geom_point(color = godfather_theme_colors["medium"]) +
  labs(title = "The Godfather theme", x = "Variable x", y = "Variable y") +
  theme_godfather(godfather_font = TRUE)
```


## Citation

### BibTeX:
```
@software{JaneBarbie2023,
  author = {Jané, Matthew B. and Pilling, Luke C. and Kenny, Christopher T.},
  month = {6},
  title = {theme_park: popular culture ggplot themes},
  url = {https://github.com/MatthewBJane/theme_park},
  version = {0.0.9},
  year = {2023}
}
```
### APA:
Jané, M.B., Pilling, Luke C., & Kenny, Christopher T. (2023). theme_park: popular culture ggplot themes (Version 0.0.9) [Source Code]. https://github.com/MatthewBJane/theme_park
